### 2025-08-05 mycv/cv_latex.tex
update

        \normalsize
        \mbox{School of Materials Science and Engineering, Changwon National University}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{mailto:yjeong@changwon.ac.kr}{yjeong@changwon.ac.kr}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{tel:+82-55-214-3694}{+82-55-214-3694}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{https://youngung.github.io/}{youngung.github.io}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{https://github.com/youngung}{github.com/youngung}}%
    \end{header}

@@

    \section{Selected recent publications}
        \begin{samepage}
            \begin{twocolentry}{2024}
                \begin{highlights}
                \item\href{https://doi.org/10.1016/j.ijplas.2024.104098}{Direct application of elasto‑viscoplastic self‑consistent crystal plasticity model to U‑draw bending and springback of dual‑phase high strength steel}
                \end{highlights}
            \end{twocolentry}
            \begin{onecolentry}
                {\it International Journal of Plasticity} 181
            \end{onecolentry}
            \begin{onecolentry}
                B. Jeon, S.-Y. Lee, J. Lee, {\underline{\textit{Y. Jeong}*}}
            \end{onecolentry}
            \vspace{0.10 cm}

@@

            \begin{twocolentry}{2020}
                \begin{highlights}
                \item\href{https://doi.org/10.1016/j.ijplas.2020.102812}{An efficient elasto‑visco‑plastic self‑consistent formulation: Application to steel subjected to loading path changes}
                \end{highlights}
            \end{twocolentry}
            \begin{onecolentry}
                {\it International Journal of Plasticity} 135
            \end{onecolentry}
            \begin{onecolentry}
                {\underline{\textit{Y. Jeong}*}}, C. N. Tomé
            \end{onecolentry}
            \vspace{0.10 cm}
        \end{samepage}

@@

    \section{Skills}
        \begin{onecolentry}
            \item Constitutive modeling: Phenomenological plasticity and crystal plasticity modeling
            \item Programming languages: Fortran, Python (NumPy, SciPy, and matplotlib), Matlab, shell scripts
            \item Languages: Korean, English
            \item Experimental Mechanics: uniaxial tension, shear, hydraulic bulge test, biaxial tests, digital image correlation (DIC)
            \item Diffraction experiments: X-ray diffraction, Electron back-scattered diffraction (EBSD), Residual stress analysis
            \item Computer skills: Linux, Git
        \end{onecolentry}

@@

        \item
          \begin{twocolentry}{Accepted}
            \href{https://doi.org/10.1016/j.ijplas.2025.104380}{Role of recovery in the microstructure development and mechanical behavior of a ductile Mg-Zn-Nd-Y-Zr alloy: an analysis using EBSD data and crystal plasticity simulations}
        \end{twocolentry}
        \begin{onecolentry}
            {\it International Journal of Plasticity}, in press
        \end{onecolentry}
        \begin{onecolentry}
            José Victoria-Hernández*, {\underline{\textit{Y. Jeong}*}}, Dietmar Letzig
        \end{onecolentry}
        \vspace{0.10 cm}

>>>>

        \normalsize
        \mbox{Department of Materials Science and Metallurgy, Changwon National University}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{mailto:yjeong@changwon.ac.kr}{yjeong@changwon.ac.kr}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{tel:+82-55-214-3694}{+82-55-214-3694}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{https://youngung.github.io/}{youngung.github.io}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{https://github.com/youngung}{github.com/youngung}}%
    \end{header}

@@

    \section{Selected recent publications}
    \begin{samepage}

            \begin{twocolentry}{2025}
                \begin{highlights}
                \item\href{https://doi.org/10.1016/j.ijplas.2025.104380}{Role of recovery in the microstructure development and mechanical behavior of a ductile Mg-Zn-Nd-Y-Zr alloy: an analysis using EBSD data and crystal plasticity simulations}
                \end{highlights}
            \end{twocolentry}
            \begin{onecolentry}
                {\it International Journal of Plasticity} 191
            \end{onecolentry}
            \begin{onecolentry}
              José Victoria-Hernández*, {\underline{\textit{Y. Jeong}*}}, Dietmar Letzig
            \end{onecolentry}
            \vspace{0.10 cm}

            \begin{twocolentry}{2024}
                \begin{highlights}
                \item\href{https://doi.org/10.1016/j.ijplas.2024.104098}{Direct application of elasto‑viscoplastic self‑consistent crystal plasticity model to U‑draw bending and springback of dual‑phase high strength steel}
                \end{highlights}
            \end{twocolentry}
            \begin{onecolentry}
                {\it International Journal of Plasticity} 181
            \end{onecolentry}
            \begin{onecolentry}
              B. Jeon, S.-Y. Lee, J. Lee, {\underline{\textit{Y. Jeong}*}}
            \end{onecolentry}
            \vspace{0.10 cm}

@@

            % \begin{twocolentry}{2020}
            %     \begin{highlights}
            %     \item\href{https://doi.org/10.1016/j.ijplas.2020.102812}{An efficient elasto‑visco‑plastic self‑consistent formulation: Application to steel subjected to loading path changes}
            %     \end{highlights}
            % \end{twocolentry}
            % \begin{onecolentry}
            %     {\it International Journal of Plasticity} 135
            % \end{onecolentry}
            % \begin{onecolentry}
            %     {\underline{\textit{Y. Jeong}*}}, C. N. Tomé
            % \end{onecolentry}
            % \vspace{0.10 cm}

        \end{samepage}

@@

    \section{Skills}
        \begin{onecolentry}
            \item Constitutive modeling: Phenomenological plasticity and crystal plasticity modeling
            \item Languages: Korean, English
            \item Computer skills: Linux, Git
            \item Programming languages: Fortran, Python (NumPy, SciPy, and matplotlib), Matlab, shell scripts
            \item Experimental Mechanics: uniaxial tension, shear, hydraulic bulge test, biaxial tests, digital image correlation (DIC)
            \item Diffraction experiments: X-ray diffraction, Electron back-scattered diffraction (EBSD), Residual stress analysis
        \end{onecolentry}

@@

        \item
          \begin{twocolentry}{2025}
            \href{https://doi.org/10.1016/j.ijplas.2025.104380}{Role of recovery in the microstructure development and mechanical behavior of a ductile Mg-Zn-Nd-Y-Zr alloy: an analysis using EBSD data and crystal plasticity simulations}
        \end{twocolentry}
        \begin{onecolentry}
            {\it International Journal of Plasticity}, 191, 104380
        \end{onecolentry}
        \begin{onecolentry}
            José Victoria-Hernández*, {\underline{\textit{Y. Jeong}*}}, Dietmar Letzig
        \end{onecolentry}
        \vspace{0.10 cm}
